SHARP - II. Mass structure in strong lenses is not necessarily substructure: A flux ratio anomaly from an edge-on disc

### 2016-02-12 papers/B1555_EdgeOn/Resubmission_v2/referee_response_2.txt

------

REFEREE: Similarly, the penultimate sentence of the abstract is also potentially misleading.  The modeling presented in this paper does not show that simple models containing disks can reproduce the observations, since those models are woefully underconstrained by the data that the authors fit.  Indeed, for the casual reader it would be useful for the text to explicitly state in words that the number of model parameters (13) exceeds the number of observational constraints (11), and that therefore the model should fit the data exactly with 2 exact parameter degeneracies.  Presumably, the weak prior on the centroid locations of the two lens components acts to break the exact degeneracy, though it is puzzling that the uncertainties on the model parameters listed in Table 3 are so much smaller than the 0.05 arcsecond prior on the centroids.  It would be useful for the text to provide an explanation for why the uncertainties on the parameters are so small, since in the absence of the centroid prior there should be 2 exact degeneracies.

We agree with the referee that the number of free parameters in original model can post a potential threat to our conclusions. We therefore follow the approach in the studies of B1600, another edge-on lens, looking at the photometry to fix the centroid positions, ellipticity, and position angle of the disc component in our best-fit model search. This reduces the number of free parameters from 13 to 9. This is the typical number of free parameters for a standard SIE plus external shear lens model, with the replacement of exponential disc component.  The predicted image positions and flux ratios in this new model still agree with the observations, which supports our original statements and conclusions. We also take off the 0.05 arcsecond prior on the centroids in the best-fit model search. The alignment between two components without using a prior implies that this centroid prior is not necessary.

Besides from the responses above, we think our work include the following new discovers hence should be published:
1) new infrared imaging with Keck and HST that show there is a disc that directly crosses the problem images.
2) new radio VLBA imaging that show the radio images are not point-sources as have been previously assumed by Dalal & Kochanek (2002) and others, and so will be less sensitive to substructure, that is, the demagnification will be felt less over the whole arc.
3) new radio VLBA imaging that show image A has a smaller angular size, relative to image B, which demonstrates that there must be a perturbation of the mass model, that is, not due to extinction (seen at optical) or absorption.
4) new estimates of the flux-ratios using the monitoring data by Koopmans et al. (2003), which was the largest source of uncertainty in the Dalal & Kochanek analysis.
5) a new mass model that includes the disc and can reproduce the observed image positions and flux-ratios without the need for substructure.
6) a potential bias in substructure analysis from flux ratio anomalous quasars due to the small size of the current sample.

### 2016-02-12 papers/B1555_EdgeOn/B1555_letter.tex
update referee response, letter to editor

Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems. \textbf{\citet{Maller97,Kee98, Moller03} have shown that a disc with high inclination angle can significantly affects the lensing cross-section. While the current sample of lensed quasars with flux ratio anomalies is fairly small, few systems with edge-on disc is sufficient to bring a bias into the substructure analysis. Moreover, near-infrared AO imaging of
other lenses in the SHARP sample shows that B1555+375 is not the only
system that has a significant disc component detection close to merging images among the current sample of flux ratio anomalous systems; these gravitational lenses will be investigated in future
work, but the images alone suggest that other systems may have similar
links between flux-ratio anomalies and disc components. This bias brought by edge-on disc may be avoided by post-selection as the sample size grows in the future. Therefore, it is critical to obtain high-resolution imaging like SHARP of target lenses to detect `sharp' mass features such as edge-on disks or even massive luminous satellites.} 
% A number of lens systems with significant disc components arealready known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}. 
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines \citep[e.g.][]{N14}.
  %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.

>>>>

Our analysis of B1555+375 demonstrates that the choice of the macromodel used to describe the `smooth' lens galaxy mass distribution, combined with the limited information provided by the position of compact lensed images, can lead to a misinterpretation of the origin of flux-ratio anomalies in some systems. \textbf{\citet{Maller97,Kee98, Moller03} have shown that a disc with high inclination angle can significantly affects the lensing cross-section. While the current sample of lensed quasars with flux ratio anomalies is fairly small, few systems with edge-on disc may be sufficient to bring a bias into the substructure analysis. Moreover, near-infrared AO imaging of
other lenses in the SHARP sample shows that B1555+375 is not the only
system that has a significant disc component detection close to merging images among the current sample of flux ratio anomalous systems; these gravitational lenses will be investigated in future
work, but the images alone suggest that other systems may have similar
links between flux-ratio anomalies and disc components. This potential bias brought by edge-on disc may be avoided by post-selection as the sample size grows in the future. Therefore, it is critical to obtain high-resolution imaging like SHARP of target lenses to detect `sharp' mass features such as edge-on disks or even massive luminous satellites.} 
% A number of lens systems with significant disc components arealready known, including, for example, the sample of 16 edge-on disks from SDSS found in the SWELLS survey \citep{swells1}. 
 This result is timely, as upcoming large-scale surveys (e.g., the Dark Energy Survey, Kilo-Degree Survey, Euclid, and the Large Synoptic Survey Telescope) will deliver orders of magnitude more gravitationally lensed quasars for which flux ratios can
  be measured using narrow lines \citep[e.g.][]{N14}.
  %Finally, we note that massive edge-on discs are \textit{not} observed in some flux-ratio anomaly systems \citep[and the presence of a disc-like component may not resolve the anomaly anyway;][]{evans03}, indicating that these systems are still useful for probing the dark matter substructure mass function.
